The contribution of blowing snow to cloud properties and the atmospheric radiative budget over Antarctica

### 2020-10-28 manuscript/manuscript.tex
WIP: results

>>>>

To explore how the macrophysical cloud properties in MAR with snow differ from the base simulation without blowing snow, we show the spatial difference in cloud cover, cloud optical depth, liquid- and ice water path in Fig.\ref{fig:micro} A-D. Overall, our results show a clear signal of increased cloud cover over most of Antarctica (\textbf{AIS: XX $\pm$ XX, Ocean: XX $\pm$ XX}). Only over parts of the Souther Ocean do we see a small decrease in clouds (Fig.\ref{fig:micro}A). Over most of Antarctica our results indicate no changes in cloud optical depth (Fig.\ref{fig:micro}B). Interestingly, over the Southern Ocean and near the Antarctic peninsula we see areas with a strong COD increase (maximum \textbf{+XX}) and strong decreases (minimum \textbf{-XX}). This strong decrease in COD over open ocean waters is mainly a result of a decrease in LWP (Fig.\ref{fig:micro}C), in addition to a decrease in IWP (Fig.\ref{fig:micro}D). This decrease in COD, CC, LWP and IWP over the open ocean could be due to a decrease in cloud lifetime because of extra ice crystal numbers due to blowing snow, potentially increasing the glaciation rate of clouds via the Wegener-Bergeron-Findeisen process (\textbf{cite Storelvmo2011, Gallee}) and subsequent increase in precipitation efficiency upstream of the Southern Ocean (\textbf{cite Storelvmo2011}).

Conversely, over the drier and colder interior of Antarctica, we see almost no changes in COD, nor in LWP, despite a significant increase in cloud cover (Fig.\ref{fig:micro}A-C). However, our results suggest a widespread increase in cloud ice water path (Fig.\ref{fig:micro}D), with a mean over the AIS of \textbf{+XX}. Here, additional airborne particles likely increase the rate of new ice growth due to the Wegener-Bergeron-Findeisen process, which states that ice particles grow at the expense of liquid cloud condensate (\textbf{CITE WBF}). In our simulations this process seems to be most efficient over the steeper margins of Antarctica, where 1) snow mass transport increases with stronger katabatic winds, where 2) turbulence mixes snow and ice to higher elevations and where 3) the chances of mixed-phase clouds increases due to an increase in oceanic influence and higher temperatures than over the interior Antarctic plateau. Additionally, new ice particles can also in MAR due to higher relative humidity of the advected air via the gas phase or via heterogeneous and homogeneous freezing (\textbf{cite Gallee}). Note however, that the MAR cloud microphysics scheme currently does not account for secondary ice production, where one single ice crystal can turn into multiple ice crystals via collision breakup, drop shattering and rime splintering (\textbf{cite Sotiropoulou, Gallee, Storelvmo2011}). However, especially rime splintering and drop shattering need liquid to be present and are most efficient in temperatures above what we observe over Antarctica (\textbf{Sotiroupoulou}). Therefore, we don't think that the missing drop shattering and rime splintering processes are a major source of uncertainty in our simulations, however, collision breakup in blowing snow clouds could be an important missing multiplier of ice crystal number concentration in our simulations.
